Confirmation of Wide-Field Signatures in Redshifted 21~cm Power Spectra using Murchison Widefield Array Observations

### 2015-04-01 ms.tex
Add more emphasis in the Summary section
From 14c8919:
============

In ms.tex,

(*) Modify Summary section to add more emphasis on the need to confirm
the pitchfork signature

The delay power spectra morphologies from data and modeling are remarkably similar even while ignoring any differences in the amplitude scales. We attribute these differences to uncertainties in the foreground model, the MWA tile power pattern, thermal fluctuations, and other uncertainties noted in \citet{thy15}.

@@

In a recent study, through the use of all-sky foreground and instrument models, the role of wide-field nature of radio interferometric measurements, hitherto unpredicted, has emerged. Referred to as the {\it pitchfork} signature in the delay spectral domain, it is characterized by significant foreground power in the primary field of view and an enhancement in power near the horizon. The latter is due to the highly nonlinear mapping between geometric delays and subtended solid angles, besides an increase in sensitivity to larger scales caused by foreshortening of baseline lengths along these directions. Owing to its localization in the delay domain, it is a leading cause of contamination in Fourier modes most sensitive to the EoR H~{\sc i} signal. This feature could not be confirmed in single MWA snapshots due to large thermal fluctuations.

By averaging 12 independent LST-aligned snapshots from MWA observations, we improve the dynamic range in delay power spectra by a factor $\gtrsim$~10 while maintaining the foreground contributions in the observed {\it visibilities} coherent. Foreground power in delay bins near the horizon is distinctly visible with a signal-noise ratio $>10$. Further, there is a close resemblance in the morphologies of delay power spectra from data and models. Together, they allow us to make a robust confirmation of the nature of wide-field measurements in EoR experiments.

>>>>

The delay power spectra morphologies from data and modeling are remarkably similar despite some differences in the amplitude scales. We attribute these differences to uncertainties in the foreground model, the MWA tile power pattern, thermal fluctuations, and other uncertainties noted in \citet{thy15}.

@@

In a recent study, through the use of all-sky foreground and instrument models, the role of wide-field nature of radio interferometric measurements, hitherto unpredicted, has emerged. Referred to as the {\it pitchfork} signature in the delay spectral domain, it is characterized by significant foreground power in the primary field of view and an enhancement in power near the horizon. The latter is due to the highly nonlinear mapping between geometric delays and subtended solid angles, besides an increase in sensitivity to larger scales caused by foreshortening of baseline lengths along these directions. Owing to its localization in the delay domain, it is a leading cause of contamination in Fourier modes most sensitive to the EoR H~{\sc i} signal.

Knowledge of these characteristics weigh heavily on choices in instrument design like antenna aperture and in data analysis such as optimal weighting schemes for future instruments such as HERA and SKA. We report the first robust detection of the {\it pitchfork} signature (which could not be confirmed earlier in single MWA snapshots due to large thermal fluctuations) with a signal-noise ratio $>10$ made possible by coherent averaging of 12 independent LST-aligned snapshots from MWA observations.

% By averaging 12 independent LST-aligned snapshots from MWA observations, we improve the dynamic range in delay power spectra by a factor $\gtrsim$~10 while maintaining the foreground contributions in the observed {\it visibilities} coherent. Foreground power in delay bins near the horizon is distinctly visible with a signal-noise ratio $>10$. Further, there is a close resemblance in the morphologies of delay power spectra from data and models. Together, they allow us to make the first robust confirmation of the nature of wide-field measurements in EoR experiments.
